Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-22 paper/paper.tex
Fix another issue
Fix typos

In the past decade software projects have inherently become more complex and they now require increasing number of developers in
the team. Studies such as the one conducted by Herbsleb \cite{herbsleb2007global} show how software engineering teams have 
transitioned from small, collocated to globally distributed teams. One reason elicited in the paper is the increasing 
popularity of communication tools, such as Slack or Google Hangouts. Due to this, developers have created issue tracking 
systems as means of planning, managing and tracking work products in the form of \emph{software tickets} or \emph{issues}.

@@

Even though tickets provide such comprehensive data regarding a specific task, studies have shown 
that fixing bugs is one of the most common and time consuming tasks performed by developers \cite{latoza2006maintaining}. One of
the reasons for this is the communication friction between developers and end users \cite{Korkala2014WasteIdentification}
as developers might need clarification regarding what information the users have provided (e.g. cannot reproduce the bug, 
screenshot is unclear). Another main reason for this waste of effort on solving tickets, according to 
Just et. al \cite{just2008towards} and Zimmermann et. al \cite{zimmermann2009improving}, is the generally poor design of issue 
tracking systems. This can lead to various issues, including increased costs for the company, wasted development effort, 
decreased customer satisfaction and overall poor performance.

@@

The study of Bettenburg et. al \cite{bettenburg2008makes} showed what 
makes for a valuable bug report through qualitative analysis. 
After conducting interviews with over 450 developers, Bettenburg et. al concluded that one of the main factors
behind a quality ticket is grammar correctness in summary and description. Another
aspect which was flagged as helpful by the interviewees was the presence of stack 
traces and steps to reproduce in tickets. A further contribution brought by the
authors to the community is the creation of a tool called Cuezilla which is able 
to automatically predict the quality of a bug report with an accuracy of around 40\%.

Another research paper that strenghtens the argument that readability is a quality 
factor in software tickets is the one presented by Hooimeijer et. al \cite{hooimeijer2007modeling}.
They conducted their analysis on over 25,000 bug reports from the Mozilla project, 
investigating readability, daily load, submitter reputation, the whole changelog histories 
and severity. They conclude that not only readability in the textual fields of a ticket
influence the \emph{Time-To-Close}, but also that the presence of attachments and 
the number of comments have a clear effect on the duration of triaging. On the 
other hand, the patch count and other similar fields did not provide significant 
value to the quality of tickets.

However, there are other types on information typically included in software tickets 
which might prove beneficial for developers and subsequently improve the ticket quality.
One such type is stack traces and Schroter et. al \cite{schroter2010stack} analyse how 
quickly tickets are closed when they either have stack traces included in their fields 
(e.g. description) or not. They collected their data from the Eclipse project using 
the InfoZilla tool proposed by Bettenburg et. al \cite{bettenburg2008extracting}.
Then, they linked the stack traces to changes in source code by mining the Eclipse version 
controlled repository. The results showed that 
around 60\% of the bugs that contained stack traces in their reports were fixed
in one of the methods in the frame. Moreover, more than 40\% of the tickets having stack traces
got fixed in the first stack frame.

Software tickets can have duplicates, usually meaning that the most important fields, such 
as summary or description, describe the same feature request or bug report. Even though 
one might believe that they cannot bring any value to a software project, the work of 
Bettenburg et. al \cite{bettenburg2008duplicate} shows the contrary.
The authors collected large amounts of data from the Eclipse open source project and ran
various kind of textual and statistical analysis on the data to find answers.
After the results were computed, they concluded that usually bug duplicates contain 
information that is not present in the master report (i.e. the original report that was 
filed). Also, developers also specified that they have often found value in these 
duplicate bug reports and that they can even aid automated triaging techniques.

Another study that investigates duplicate bug reports is the work conducted by Prifti et. al \cite{prifti2011detecting}. 
The authors first collected 75,000 bug reports from Bugzilla for the Firefox project. Then, they created a tool 
for detecting bug report duplicates with an accuracy of 53\%. However, due to prior 
findings showing both that duplicate reports can improve the quality \cite{bettenburg2008duplicate}
but also decrease it \cite{cavalcanti2013bug}, this study tries to achieve a middle ground - 
before the reporter can file the bug in the system, the duplicate detection tool previously 
described runs and checks whether there are any duplicates. If there are, the user is presented 
with the possibility of simply adding extra information, if suitable, to one of the duplicates 
found. This is indeed a novel approach that can bring great benefits to the software engineering 
community and the authors state that they wish to pursue future work on this idea.

Bettenburg et. al \cite{bettenburg2012using} present in their work an application
called infoZilla. This tool can
parse bug reports and correctly extract stack traces, patches and source code. 
When evaluated on over 150,000 bug reports, it proved to have a very high rate of over 97\% accuracy.
We applied some of the techniques shown in the study and successfully managed to 
retrieve stack traces as well with a great accuracy.

The first information to be filled in by end users or developers on any issue tracking system
is the summary field, which holds a small description, usually between 5 and 30 words, of 
the request or bug being reported. In the study conducted by Rastkar et. al \cite{rastkar2010summarizing}, 
the authors investigated whether tickets could be summarized automatically and efficiently. What 
that implies is that developers would not be required to look at complete tickets comprised 
of a large number of fields, but rather at a simple summary of a couple of lines 
encapsulating the whole information. The authors selected the Mozilla, Eclipse, Gnome and KDE 
open source projects and then they asked volunteering university students to annotate 
the tickets in the issue tracking systems. More specifically, they had to write a summary 
of maximum 250 words using both technical and non-technical terms, depending on their expertise. 
Then, the study presents Machine Learning algorithms employed to parse these summaries and 
learn how to efficiently create automated summaries for new bug reports. Afterwards, they asked 
software developers to rate these auto-generated summaries against the original ones and 
the conclusion was that existing conversation-based extractive summary generators used 
for software tickets produce the best results.

The work of Just et. al \cite{just2008towards} examines a rather different aspect
of quality in tickets - they are investigating the quality of the underlying issue 
tracking systems instead. 
The authors ran a survey on 175 developers from Eclipse, Apache and Mozilla
Then, they applied a card sort in order to organize the comments into hierarchies to 
identify common patterns. Their findings can be summarized in the following top seven
suggestions:
  \begin{itemize}
    \item create differentiation between bug report difficulty levels between 
    novices and experiences reporters;
    \item encourage users to input as much information as possible;
    \item add ability to merge tickets when needed;
    \item recognise and reward valuable bug reporters;
    \item integrate reputation into user profiles to mark experienced reporters;
    \item to be able to easily and expressively search through tickets.
  \end{itemize}

Having discussed about various factors that can influence the quality in software tickets, 
we also need to take into account how can we apply this knowledge to solving the issue of 
poor design in issue tracking systems and how the ticket creation process could be improved. 
The study conducted by Lamkanfi et. al \cite{lamkanfi2010predicting} looks at this aspect and
shows how issue tracking systems could be extended in order to automatically generate the severity 
of a ticket (e.g. assign story points to a Jira issue). The authors conducted their research on the Mozilla,
GNOME and Eclipse and projects and split their approach into four steps: extract and organize tickets, 
pre-process tickets (i.e. tokenization, stop word removal and stemming), train the classifier on two datasets 
of tickets - 70\% training and 30\% evaluation and apply the trained classifier on the evaluation set.
The conclusions they drew from running the evaluation process were rather 
interesting:
  \begin{itemize}
    \item terms such as segfault, deadlock, crash, hand or memory typically indicate
      a severe bug;
    \item when analyzing the textual description they found that using simple
      one line summaries resulted in less false positives and increased precision
      levels;
    \item the classifier needs a large number of tickets in order to predict correctly;
    \item depending on how well a software project is modularised, one can 
      use a predictor per module rather than a universal one.
  \end{itemize}

Another overall aspect of software tickets and issue tracking systems that could be improved through 
determining the quality factors for tickets is automatically assigning a bug report or a feature request 
to the most suitable developer (or team of developers). Anvik et. al \cite{anvik2011reducing}
propose a Machine Learning technique that could automatically assign a bug report to the developer 
with the most expertise in that specific area. Firstly, the algorithm takes as input various types of information from 
tickets: textual description and summary, operating system used when the bug occurred, developer 
who owns the source code, which developers have lighter workloads at that point in time etc. After the 
tool was evaluated, the authors concluded that it can be used in production as it provides a high 
rate of accuracy when assigning the developers, but it needs more data so that the model is trained 
properly.

@@

Then, the analysis routine runs in parallel the \emph{seven types of analysis} for answering the research questions 
outlied in Section \ref{intro}, each in its own separate goroutine in order to speed up the process:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence time-to-close the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the time-to-close of a ticket; the regular expression was adapted after the general guidelines elicited by 
  Bettenburg et. al \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
  steps to reproduce are a subset);
  \item \emph{stack traces} - runs complex regex for detecting exception stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket; this analysis only inspects projects
  written in Java as it is the most popular proponent built-in of stack traces;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  the number of words in comments has an impact on the Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description wordiness;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
  positive);
\end{itemize}

@@

More specifically, we computed the following numbers for the tickets we collected:
\begin{itemize}
  \item out of the 303,138 tickets, 236,383 tickets have been closed (i.e. marked Closed, Resolved, Done or Completed) by the time we 
  fetched them from the Jira instance;
  \item 287,120 tickets are of high priority (i.e. marked as Blocker, Critical, Major or High);
  \item 201,786 tickets have all our requirements for running the analysis: were closed by the time we fetched the data, 
  are of high priority and are not \emph{wrong} values retrieved from Jira (i.e. outliers);
  \item 103,397 tickets have attachments which we split in the following categories:
    \begin{itemize}
      \item 4,082 have code attachments (e.g. Go, Java, Python);
      \item 7,171 have image attachments (e.g. png, jpg/jpeg, gif);
      \item 164 have video attachments (e.g. mkv, avi, mp4);
      \item 13,990 have text attachments (e.g. txt, md, doc(x));
      \item 918 have config attachments (e.g. json, xml, yml);
      \item 2,491 have archive attachments (e.g. zip, tar.gz, rar, 7z);
      \item 280 have spreadsheet attachments (e.g. csv, xlsx);
      \item 80,015 have other attachments (i.e. any file extension not pre-defined by us in one of the above categories).
    \end{itemize}
  \item 270,907 tickets have comments;
  \item 39,988 tickets have steps to reproduce (i.e. sequence of steps specified by the bug reporter that would reproduce a certain bug); 
  we applied the general guidelines described by Bettenburg et. al \cite{bettenburg2008extracting} on how to extract structured 
  data (including steps to reproduce) from tickets in order to create a regular expression for capturing them;
  \item 1,942 tickets have Java stack traces - we have applied the technique described by Bettenburg et. al 
  \cite{bettenburg2008extracting} for extracting structured data from bug reports and even though the method proved to be efficient, 
  the total number of stack traces is so small due to the fact that many projects are actually written in languages other than Java;
  \item 133,689 tickets have grammar correctness scores (i.e. number of grammar mistakes inside summary, description and comments) - 
  they have been collected using Microsoft Azure Bing Spell Check API which is one of the best grammar checking tool in the industry; 
  \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description
  and comments) - they have been collected using Google Cloud Platform Natural Language Processing APIs.
\end{itemize}

@@

For this analysis, we only looked at tickets of high priority, closed and the project they correspond 
is written in Java. In total, we investigated looked at We then ran a complex regular expression derived from the works of Bettenburg et. al 
\cite{bettenburg2012using} and Moreno et. al \cite{moreno2014use} and collected all the tickets that have 
stack traces. In the end, we got a total number of 256 tickets that had at least an exception stack trace 
attached in either summary, description or any of the comments.

@@

Even though this might be surprising at first, we need to analyse the possible context where such large 
number of words in comments occur. What if the bug was so hard to reproduce that the developers needed to 
ask more than one user how they experienced the issue in the tool? Another case might be that even though 
the comments start by discussing fixing or implementing a feature, the developers and end users might 
engage in new conversations about the product in general or other features that they might want to see 
implemented. Also, what if comments are a means of communication for developers in the team? There are studies, 
such as the one conducted by Lotufo et. al \cite{lotufo2015modelling}, that show the importance of comments 
in software tickets in relation to communication activities surrounding the project. Another possible explanation 
for having increased number of comments increase the Time-To-Close value and, thus, decrease quality, is that 
having many comments or very verbose comment can lead to more difficult information extraction. On the other 
hand, if there would be a light discussion, the developers would be able to quickly analyse all the comments 
and collect whatever is necessary to resolve the ticket.

@@

This is not a surprise - as previously mentioned, summary and description are the core components of any ticket. 
As summary is described by Jira, it should represent a short textual description of the bug or the feature request. However,
we have identified tickets having summaries with even more than 200 words. This is not optimal and might obfuscate
the essential reason of filing that ticket from triagers and developers working on the project. One of the findings 
Zimmermann et. al \cite{zimmermann2010makes} present in their study is that a good, succint summary can significantly 
reduce the effort invested by the developers.

@@

Through calling Microsoft Azure's Bing Spell Check API, one of the best grammar analysis APIs in the industry, we 
managed to calculate the total number of grammar errors in summary, description and comments for a total number 
of 133,689 tickets. As shown in a number of studies, the number of spelling errors can influence the quality of a ticket. 
However, in the work conducted by Schugerl et. al \cite{schugerl2008mining}, the authors found that spelling errors 
can be found in both high and low quality tickets, thus should not be considered as a reliable factor for determining
the Time-To-Close for a ticket. In the rest of this section we will demonstrate the contrary - tickets with more 
grammar errors (spelling errors are just a subset of the types of errors we are investigating) imply lower quality
tickets (i.e. increased time-to-close).

@@

On the other side of the spectrum, having a more positive score leads to reduced time-to-close values for tickets. Calefato et. al 
\cite{calefato2015mining} conducted a study where they show that a positive sentiment has the biggest impact on 
the quality of an answer on Stack Overflow, one of the most popular websites related to programming in general. This 
implies that when developers and triagers treat their reporters respectfully and offer support whenever possible, 
the users will feel more welcomed and willing to help report other bugs in the future as well. We also have scores of 
over 0.9, meaning that the actors participating in the discussion (or the reported summary/description) might compliment 
each other for doing a great job.

@@

Furthermore, the project could greatly benefit from having access to closed source repositories in addition to the 
open source ones. Most closed source projects have much more structured planning, tracking and management activities - as 
Crowston et. al \cite{crowston2012free} present in their study, open source projects lack organized coordination which,
in the context of our study, means that people do not invest much effort into properly creating tickets in issue tracking 
systems, triaging efficiently, planning the work and tracking it. On the other hand, closed source projects follow 
more strict guidelines: standard working hours (would make tracking and linking the source code changes to tickets easier), 
adding story points (i.e. adding estimated difficulty or time to complete) and properly planning tickets before work 
starts on the task, tickets properly distributed to developers based on availability and expertise etc. These benefits 
of closed source projects would prove helpful for our analysis.

@@

A major future work candidate is availability of a technique to calculate the difficulty of a ticket based on the information
inside it. Unfortunately, at the moment, the research community has not come up with such an approach. 
Vijayakumar et. al \cite{vijayakumar2014much} proposed a method of predicting how much effort is required for fixing 
a bug, but after running it on our data, it did not prove successful. After such a technique becomes available, we could 
incorporate it inside our tool and group the tickets compared in all analysis types based on their difficulty in order to 
have better results.

>>>>

In the past decade software projects have inherently become more complex and they now require an increasing number of developers 
on the team. Studies such as the one conducted by Herbsleb \cite{herbsleb2007global} show how software engineering teams have 
transitioned from small, collocated to globally distributed teams. One reason elicited in the paper is the increasing 
popularity of communication tools, such as Slack or Google Hangouts. Due to this, developers have created issue tracking 
systems as means of planning, managing and tracking work products in the form of \emph{software tickets} or \emph{issues}.

@@

Even though tickets provide such comprehensive data regarding a specific task, evidence shows 
that fixing bugs is one of the most common and time consuming tasks performed by developers \cite{latoza2006maintaining}. One of
the reasons for this is the communication friction between developers and end users \cite{Korkala2014WasteIdentification}
as developers might need clarification regarding what information the users have provided (e.g. cannot reproduce the bug, 
screenshot is unclear). Another main reason for this waste of effort on solving tickets, according to 
Just et al. \cite{just2008towards} and Zimmermann et al. \cite{zimmermann2009improving}, is the generally poor design of issue 
tracking systems. This can lead to various issues, including increased costs for the company, wasted development effort, 
decreased customer satisfaction and overall poor performance.

@@

The study of Bettenburg et al. \cite{bettenburg2008makes} showed what 
makes for a valuable bug report through qualitative analysis. 
After conducting interviews with over 450 developers, Bettenburg et al. concluded that one of the main factors
behind a quality ticket is grammar correctness in summary and description. Another
aspect which was flagged as helpful by the interviewees was the presence of stack 
traces and steps to reproduce in tickets. A further contribution brought by the
authors to the community is the creation of a tool called Cuezilla which is able 
to automatically predict the quality of a bug report with an accuracy of around 40\%.

Another research paper that strenghtens the argument that readability is a quality 
factor in software tickets is the one presented by Hooimeijer et al. \cite{hooimeijer2007modeling}.
They conducted their analysis on over 25,000 bug reports from the Mozilla project, 
investigating readability, daily load, submitter reputation, the whole changelog histories 
and severity. They conclude that not only readability in the textual fields of a ticket
influence the \emph{Time-To-Close}, but also that the presence of attachments and 
the number of comments have a clear effect on the duration of triaging. On the 
other hand, the patch count and other similar fields did not provide significant 
value to the quality of tickets.

However, there are other types on information typically included in software tickets 
which might prove beneficial for developers and subsequently improve the ticket quality.
One such type is stack traces and Schroter et al. \cite{schroter2010stack} analyse how 
quickly tickets are closed when they either have stack traces included in their fields 
(e.g. description) or not. They collected their data from the Eclipse project using 
the InfoZilla tool proposed by Bettenburg et al. \cite{bettenburg2008extracting}.
Then, they linked the stack traces to changes in source code by mining the Eclipse version 
controlled repository. The results showed that 
around 60\% of the bugs that contained stack traces in their reports were fixed
in one of the methods in the frame. Moreover, more than 40\% of the tickets having stack traces
got fixed in the first stack frame.

Software tickets can have duplicates, usually meaning that the most important fields, such 
as summary or description, describe the same feature request or bug report. Even though 
one might believe that they cannot bring any value to a software project, the work of 
Bettenburg et al. \cite{bettenburg2008duplicate} shows the contrary.
The authors collected large amounts of data from the Eclipse open source project and ran
various kind of textual and statistical analysis on the data to find answers.
After the results were computed, they concluded that usually bug duplicates contain 
information that is not present in the master report (i.e. the original report that was 
filed). Also, developers also specified that they have often found value in these 
duplicate bug reports and that they can even aid automated triaging techniques.

Another study that investigates duplicate bug reports is the work conducted by Prifti et al. \cite{prifti2011detecting}. 
The authors first collected 75,000 bug reports from Bugzilla for the Firefox project. Then, they created a tool 
for detecting bug report duplicates with an accuracy of 53\%. However, due to prior 
findings showing both that duplicate reports can improve the quality \cite{bettenburg2008duplicate}
but also decrease it \cite{cavalcanti2013bug}, this study tries to achieve a middle ground - 
before the reporter can file the bug in the system, the duplicate detection tool previously 
described runs and checks whether there are any duplicates. If there are, the user is presented 
with the possibility of simply adding extra information, if suitable, to one of the duplicates 
found. This is indeed a novel approach that can bring great benefits to the software engineering 
community and the authors state that they wish to pursue future work on this idea.

Bettenburg et al. \cite{bettenburg2012using} present in their work an application
called infoZilla. This tool can
parse bug reports and correctly extract stack traces, patches and source code. 
When evaluated on over 150,000 bug reports, it proved to have a very high rate of over 97\% accuracy.
We applied some of the techniques shown in the study and successfully managed to 
retrieve stack traces as well with a great accuracy.

The first information to be filled in by end users or developers on any issue tracking system
is the summary field, which holds a small description, usually between 5 and 30 words, of 
the request or bug being reported. In the study conducted by Rastkar et al. \cite{rastkar2010summarizing}, 
the authors investigated whether tickets could be summarized automatically and efficiently. What 
that implies is that developers would not be required to look at complete tickets comprised 
of a large number of fields, but rather at a simple summary of a couple of lines 
encapsulating the whole information. The authors selected the Mozilla, Eclipse, Gnome and KDE 
open source projects and then they asked volunteering university students to annotate 
the tickets in the issue tracking systems. More specifically, they had to write a summary 
of maximum 250 words using both technical and non-technical terms, depending on their expertise. 
Then, the study presents Machine Learning algorithms employed to parse these summaries and 
learn how to efficiently create automated summaries for new bug reports. Afterwards, they asked 
software developers to rate these auto-generated summaries against the original ones and 
the conclusion was that existing conversation-based extractive summary generators used 
for software tickets produce the best results.

The work of Just et al. \cite{just2008towards} examines a rather different aspect
of quality in tickets - they are investigating the quality of the underlying issue 
tracking systems instead. 
The authors ran a survey on 175 developers from Eclipse, Apache and Mozilla
Then, they applied a card sort in order to organize the comments into hierarchies to 
identify common patterns. Their findings can be summarized in the following top seven
suggestions:
  \begin{itemize}
    \item create differentiation between bug report difficulty levels between 
    novices and experiences reporters;
    \item encourage users to input as much information as possible;
    \item add ability to merge tickets when needed;
    \item recognise and reward valuable bug reporters;
    \item integrate reputation into user profiles to mark experienced reporters;
    \item to be able to easily and expressively search through tickets.
  \end{itemize}

Having discussed about various factors that can influence the quality in software tickets, 
we also need to take into account how can we apply this knowledge to solving the issue of 
poor design in issue tracking systems and how the ticket creation process could be improved. 
The study conducted by Lamkanfi et al. \cite{lamkanfi2010predicting} looks at this aspect and
shows how issue tracking systems could be extended in order to automatically generate the severity 
of a ticket (e.g. assign story points to a Jira issue). The authors conducted their research on the Mozilla,
GNOME and Eclipse and projects and split their approach into four steps: extract and organize tickets, 
pre-process tickets (i.e. tokenization, stop word removal and stemming), train the classifier on two datasets 
of tickets - 70\% training and 30\% evaluation and apply the trained classifier on the evaluation set.
The conclusions they drew from running the evaluation process were rather 
interesting:
  \begin{itemize}
    \item terms such as segfault, deadlock, crash, hand or memory typically indicate
      a severe bug;
    \item when analyzing the textual description they found that using simple
      one line summaries resulted in less false positives and increased precision
      levels;
    \item the classifier needs a large number of tickets in order to predict correctly;
    \item depending on how well a software project is modularised, one can 
      use a predictor per module rather than a universal one.
  \end{itemize}

Another overall aspect of software tickets and issue tracking systems that could be improved through 
determining the quality factors for tickets is automatically assigning a bug report or a feature request 
to the most suitable developer (or team of developers). Anvik et al. \cite{anvik2011reducing}
propose a Machine Learning technique that could automatically assign a bug report to the developer 
with the most expertise in that specific area. Firstly, the algorithm takes as input various types of information from 
tickets: textual description and summary, operating system used when the bug occurred, developer 
who owns the source code, which developers have lighter workloads at that point in time etc. After the 
tool was evaluated, the authors concluded that it can be used in production as it provides a high 
rate of accuracy when assigning the developers, but it needs more data so that the model is trained 
properly.

@@

Then, the analysis routine runs in parallel the \emph{seven types of analysis} for answering the research questions 
outlied in Section \ref{intro}, each in its own separate goroutine in order to speed up the process:
\begin{itemize}
  \item \emph{attachments} - checks whether attachments influence Time-To-Close and also look at what types 
  of attachments (e.g. screenshots, archive, code snippets) influence time-to-close the most;
  \item \emph{steps to reproduce} - performs a complex regex to detect steps to reproduce and then checks whether their presence
  influence the time-to-close of a ticket; the regular expression was adapted after the general guidelines elicited by 
  Bettenburg et al. \cite{bettenburg2008extracting} on how to extract structured data, including enumerations (of which 
  steps to reproduce are a subset);
  \item \emph{stack traces} - runs complex regex for detecting exception stack traces in either summary, description or comments 
  and verifies whether their presence influence Time-To-Close for the ticket; this analysis only inspects projects
  written in Java as it is the most popular proponent built-in of stack traces;
  \item \emph{comments complexity} - loops through all comments and counts all words; then, the tool verifies whether 
  the number of words in comments has an impact on the Time-To-Close for the ticket;
  \item \emph{fields complexity} - same analysis as comments complexity, but only for summary and description wordiness;
  \item \emph{grammar correctness} - it uses Azure Cloud Bing Spell Check API to perform analysis on summary, 
  description and comments; after concatenating everything and making it compatible with the API allowed formats, the tool 
  receives back in the JSON payload not only the number of flagged tokens (i.e. grammar errors), but also their types 
  (e.g. unknown token, misspell);
  \item \emph{sentiment} - uses Google Cloud Platform's Natural Language Processing API to retrieve the 
  sentiment score for summary, description and comments; it first concatenates everything and makes it conform to Google's 
  API and then sends the request, receiving a score from -1 to 1 inclusive (-1 means most negative, 1 means most 
  positive);
\end{itemize}

@@

More specifically, we computed the following numbers for the tickets we collected:
\begin{itemize}
  \item out of the 303,138 tickets, 236,383 tickets have been closed (i.e. marked Closed, Resolved, Done or Completed) by the time we 
  fetched them from the Jira instance;
  \item 287,120 tickets are of high priority (i.e. marked as Blocker, Critical, Major or High);
  \item 201,786 tickets have all our requirements for running the analysis: were closed by the time we fetched the data, 
  are of high priority and are not \emph{wrong} values retrieved from Jira (i.e. outliers);
  \item 103,397 tickets have attachments which we split in the following categories:
    \begin{itemize}
      \item 4,082 have code attachments (e.g. Go, Java, Python);
      \item 7,171 have image attachments (e.g. png, jpg/jpeg, gif);
      \item 164 have video attachments (e.g. mkv, avi, mp4);
      \item 13,990 have text attachments (e.g. txt, md, doc(x));
      \item 918 have config attachments (e.g. json, xml, yml);
      \item 2,491 have archive attachments (e.g. zip, tar.gz, rar, 7z);
      \item 280 have spreadsheet attachments (e.g. csv, xlsx);
      \item 80,015 have other attachments (i.e. any file extension not pre-defined by us in one of the above categories).
    \end{itemize}
  \item 270,907 tickets have comments;
  \item 39,988 tickets have steps to reproduce (i.e. sequence of steps specified by the bug reporter that would reproduce a certain bug); 
  we applied the general guidelines described by Bettenburg et al. \cite{bettenburg2008extracting} on how to extract structured 
  data (including steps to reproduce) from tickets in order to create a regular expression for capturing them;
  \item 1,942 tickets have Java stack traces - we have applied the technique described by Bettenburg et al. 
  \cite{bettenburg2008extracting} for extracting structured data from bug reports and even though the method proved to be efficient, 
  the total number of stack traces is so small due to the fact that many projects are actually written in languages other than Java;
  \item 133,689 tickets have grammar correctness scores (i.e. number of grammar mistakes inside summary, description and comments) - 
  they have been collected using Microsoft Azure Bing Spell Check API which is one of the best grammar checking tool in the industry; 
  \item 157,047 tickets have sentiment scores (i.e. positive/negative sentiment on a scale from -1 to 1 drawn from summary, description
  and comments) - they have been collected using Google Cloud Platform Natural Language Processing APIs.
\end{itemize}

@@

For this analysis, we only looked at tickets of high priority, closed and the project they correspond 
is written in Java. In total, we investigated looked at We then ran a complex regular expression derived from the works of Bettenburg et al. 
\cite{bettenburg2012using} and Moreno et al. \cite{moreno2014use} and collected all the tickets that have 
stack traces. In the end, we got a total number of 256 tickets that had at least an exception stack trace 
attached in either summary, description or any of the comments.

@@

Even though this might be surprising at first, we need to analyse the possible context where such large 
number of words in comments occur. What if the bug was so hard to reproduce that the developers needed to 
ask more than one user how they experienced the issue in the tool? Another case might be that even though 
the comments start by discussing fixing or implementing a feature, the developers and end users might 
engage in new conversations about the product in general or other features that they might want to see 
implemented. Also, what if comments are a means of communication for developers in the team? There are studies, 
such as the one conducted by Lotufo et al. \cite{lotufo2015modelling}, that show the importance of comments 
in software tickets in relation to communication activities surrounding the project. Another possible explanation 
for having increased number of comments increase the Time-To-Close value and, thus, decrease quality, is that 
having many comments or very verbose comment can lead to more difficult information extraction. On the other 
hand, if there would be a light discussion, the developers would be able to quickly analyse all the comments 
and collect whatever is necessary to resolve the ticket.

@@

This is not a surprise - as previously mentioned, summary and description are the core components of any ticket. 
As summary is described by Jira, it should represent a short textual description of the bug or the feature request. However,
we have identified tickets having summaries with even more than 200 words. This is not optimal and might obfuscate
the essential reason of filing that ticket from triagers and developers working on the project. One of the findings 
Zimmermann et al. \cite{zimmermann2010makes} present in their study is that a good, succint summary can significantly 
reduce the effort invested by the developers.

@@

Through calling Microsoft Azure's Bing Spell Check API, one of the best grammar analysis APIs in the industry, we 
managed to calculate the total number of grammar errors in summary, description and comments for a total number 
of 133,689 tickets. As shown in a number of studies, the number of spelling errors can influence the quality of a ticket. 
However, in the work conducted by Schugerl et al. \cite{schugerl2008mining}, the authors found that spelling errors 
can be found in both high and low quality tickets, thus should not be considered as a reliable factor for determining
the Time-To-Close for a ticket. In the rest of this section we will demonstrate the contrary - tickets with more 
grammar errors (spelling errors are just a subset of the types of errors we are investigating) imply lower quality
tickets (i.e. increased time-to-close).

@@

On the other side of the spectrum, having a more positive score leads to reduced time-to-close values for tickets. Calefato et al. 
\cite{calefato2015mining} conducted a study where they show that a positive sentiment has the biggest impact on 
the quality of an answer on Stack Overflow, one of the most popular websites related to programming in general. This 
implies that when developers and triagers treat their reporters respectfully and offer support whenever possible, 
the users will feel more welcomed and willing to help report other bugs in the future as well. We also have scores of 
over 0.9, meaning that the actors participating in the discussion (or the reported summary/description) might compliment 
each other for doing a great job.

@@

Furthermore, the project could greatly benefit from having access to closed source repositories in addition to the 
open source ones. Most closed source projects have much more structured planning, tracking and management activities - as 
Crowston et al. \cite{crowston2012free} present in their study, open source projects lack organized coordination which,
in the context of our study, means that people do not invest much effort into properly creating tickets in issue tracking 
systems, triaging efficiently, planning the work and tracking it. On the other hand, closed source projects follow 
more strict guidelines: standard working hours (would make tracking and linking the source code changes to tickets easier), 
adding story points (i.e. adding estimated difficulty or time to complete) and properly planning tickets before work 
starts on the task, tickets properly distributed to developers based on availability and expertise etc. These benefits 
of closed source projects would prove helpful for our analysis.

@@

A major future work candidate is availability of a technique to calculate the difficulty of a ticket based on the information
inside it. Unfortunately, at the moment, the research community has not come up with such an approach. 
Vijayakumar et al. \cite{vijayakumar2014much} proposed a method of predicting how much effort is required for fixing 
a bug, but after running it on our data, it did not prove successful. After such a technique becomes available, we could 
incorporate it inside our tool and group the tickets compared in all analysis types based on their difficulty in order to 
have better results.
